%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}                % to get all AMS symbols
\usepackage{amsfonts}               % basic math fonts
\usepackage{amsmath}                % AMS math macros
\usepackage{graphicx}               % to insert figures
\usepackage{xcolor}                 % colors for e-copies
\usepackage{algpseudocode}          % pseudo code and algorithms
\usepackage{subcaption}             % subfigures
\usepackage{placeins}               % Float barriers
\usepackage{hyperref}               % PDF hyperreferences
\usepackage{booktabs}

\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
\definecolor{blue(ncs)}{rgb}{0.0, 0.53, 0.74}
\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}

\DeclareMathOperator{\diag}{diag}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Preamble  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Local Fourier Analysis of Domain Decomposition and Multigrid Methods for High-Order Matrix-Free Finite Elements}

\author{Jeremy~L.}{Thompson}

\otherdegrees{B.S., United States Air Force Academy, 2009\\
	          M.Sc., University of Washington, 2011}

\degree{Doctor of Philosophy}       %  #1 {long descr.}
	   {Ph.D., Applied Mathematics} %  #2 {short descr.}

\dept{Department of}                %  #1 {designation}
	 {Applied Mathematics}          %  #2 {name}

\advisor{Prof.}                     %  #1 {title}
	    {Jed Brown}                 %  #2 {name}

\reader{Adrianna Gillman}           %  2nd person to sign thesis
\readerThree{Ian Grooms}            %  3rd person to sign thesis
\readerFour{Kenneth Jansen}         %  4th person to sign thesis

\abstract{ %\OnePageChapter	% if this abstract goes under 1 page
High-order matrix-free finite element operators offer superior performance on modern high performance computing hardware when compared to assembled sparse matrices, both with respect to floating point operations needed for operator evaluation and the memory transfer needed for a matrix-vector product.
However, high-order matrix-free operators require iterative solvers, such as Krylov subspace methods, and these methods converge slowly for ill-conditioned operators, such as high-order finite element operators.
Preconditioning techniques can improve the converge of these iterative solvers for high-order matrix-free finite element operators.
In particular, p-multigrid and domain decomposition methods are particularly well suited for problems on unstructured meshes, but these methods have parameters that require careful tuning to ensure proper convergence.
Local Fourier Analysis of these preconditioners analyzes the frequency modes found in the error on each iteration and can provide sharp convergence estimates.

We present a representation of arbitrary second-order partial differential equations for high-order finite element discretizations that facilitates matrix-free implementation.
This representation is used by the Center for Efficient Exascale Discretizations to provide performance portable high-order matrix-free implementations of finite element operators for arbitrary second order partial differential equations.

We develop Local Fourier Analysis of finite element operators represented in this fashion, focusing on multigrid and domain decomposition preconditioning techniques.
The performance of p-multigrid in parallel is partially determined by the number of multigrid levels.
A larger number of multigrid levels requires additional global communication on parallel machines, but aggressive coarsening that is not supported by the smoother in the multigrid method can lead to gaps in the error frequency modes targeted by the total multigrid method, which results in degraded convergence.
Balancing Domain Decomposition by Constraints can be used by a smoother to target a wider range of error mode frequencies and facilitate more aggressive coarsening.
We provide Local Fourier Analysis of p-multigrid with Balancing Domain Decomposition by Constraints smoothing to demonstrate the suitability of this smoother for aggressive coarsening.

Finally, we demonstrate the suitability of high-order matrix-free finite element operators with p-multigrid with Balancing Domain Decomposition by Constraints for practical problems at scale on modern parallel hardware by demonstrating the performance of these techniques on a solid mechanics problem with Neo-Hookean hyperelasticity at finite strain.
}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
This work is supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of two U.S. Department of Energy organizations (Office of Science and the National Nuclear Security Administration) responsible for the planning and preparation of a capable exascale ecosystem, including software, applications, hardware, advanced system engineering and early testbed platforms, in support of the nation’s exascale computing imperative.
}

%\ToCisShort % use this only for 1-page Table of Contents

\LoFisShort  % use this only for 1-page Table of Figures
% \emptyLoF  % use this if there is no List of Figures

\LoTisShort  % use this only for 1-page Table of Tables
% \emptyLoT  % use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  DOCUMENT  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input 01-Introduction/introduction.tex
\input 02-HighOrderFEM/highorderfem.tex
\input 03-LocalFourierAnalysis/localfourieranalysis.tex
\input 04-DomainDecomposition/domaindecomposition.tex
\input 05-MultigridMethods/multigridmethods.tex
\input 06-Conclusions/conclusions.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Bibliography  %%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}           % or "siam", or "alpha", etc.
\nocite{*}                          % list all refs in database, cited or not
\bibliography{references}           % Bib database in "refs.bib"

%%%%%%%%%%%%%%%%%%%%%%%%%%%  Appendices  %%%%%%%%%%%%%%%%%%%%%%%%%%%
%\appendix
%\input appendixA.tex
%\input appendixB.tex

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
