Both $h$-multigrid and $p$-multigrid follow the same general algorithm, with differences in the grid transfer operators and coarse grid representation.
Application of multigrid follows the algorithm given by Definition \ref{def:multigrid_algorithm}, similar to the presentation in \cite{brandt1982guide}.
\begin{definition}[Multigrid Algorithm]\label{def:multigrid_algorithm}
~\\
\begin{algorithmic}[1]
\State Compute $\mathbf{u}_k$
\State $\mathbf{u}_k \gets \mathbf{u}_k + \hat{\mathbf{M}}^{-1} \left( \mathbf{b} - {\color{burgundy}\mathbf{A}}_f \mathbf{u}_k \right)$ \Comment{pre-smooth $\nu$ times}
\State $\mathbf{r} = {\color{burgundy}\mathbf{R}}_{\text{ftoc}} \left( \mathbf{b} - {\color{burgundy}\mathbf{A}}_f \mathbf{u}_k \right)$ \Comment{restrict the residual}
\State ${\color{burgundy}\mathbf{A}}_c \mathbf{e} = \mathbf{r}$                                                                          \Comment{Solve on coarse grid (may involve additional levels)}
\State $\mathbf{u}_k \gets \mathbf{u}_k + {\color{burgundy}\mathbf{P}}_{\text{ctof}} \mathbf{e}$                                         \Comment{prolong error correction}
\State $\mathbf{u}_k \gets \mathbf{u}_k + \hat{\mathbf{M}}^{-1} \left( \mathbf{b} - {\color{burgundy}\mathbf{A}}_f \mathbf{u}_k \right)$ \Comment{post-smooth $\nu$ times}
\end{algorithmic}
\end{definition}
In this algorithm, ${\color{burgundy}\mathbf{A}}_f$ is the operator on the fine grid, ${\color{burgundy}\mathbf{P}}_{\text{ctof}}$ is the coarse to fine grid prolongation operator, ${\color{burgundy}\mathbf{R}}_{\text{ftoc}}$ the fine to coarse grid restriction operator, $\hat{\mathbf{M}}$ a separate preconditioner used for smoothing, and ${\color{burgundy}\mathbf{A}}_c$ represents solving the error correction problem on the coarse grid, which may involve recursively applying the multigrid algorithm.

For $h$-multigrid, the restriction operator represents aggregating multiple fine grid elements into larger coarse grid elements and the prolongation operator is given by the transpose.
This process requires knowledge about neighboring elements on the mesh and can be complex on fully unstructured meshes and complex geometry.

For $p$-multigrid with nodal bases, the prolongation operator interpolates from the coarse grid to the fine grid, evaluating the lower-order basis functions on the higher-order basis nodes.
Prolongation to a basis with a polynomial order that is a single order higher than the coarse grid basis is defined by
\begin{equation}
\mathbf{P}_{p - 1}^p = \Lambda \left( m_p^{-1} \right) \mathcal{E}_p^T \sum_e \mathbf{N}_{p - 1}^p \mathcal{E}^e_{p - 1},
\label{mg_prolong}
\end{equation}
where $\mathbf{N}_{p - 1}^p$ interpolates from a basis of degree $p - 1$ to degree $p$ and $m_p = \mathcal{E}_p^T \mathcal{E}_p 1$ counts the multiplicity of shared nodes between elements.
To preserve symmetry and prevent aliasing, the restriction operator is defined as the transpose of the prolongation operator, $\mathbf{R}_{p - 1}^p = \left( \mathbf{P}_{p - 1}^p \right)^T$.
These operators can be implemented in a matrix-free fashion.

Even with modest order finite elements, such as degree $4$, $p$-multigrid can substantially reduce the size of the global solution vector, by a factor of approximately $\left( p + 1 \right)^3 / 8$.
Thus, assembly of the finite element operator on the coarse grid, ${\color{burgundy}\mathbf{A}}_c$, becomes tractable and direct solvers such as AMG can be used to solve the coarse problem.