%-------------------------------------------------------------------------------
\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}                % to get all AMS symbols
\usepackage{amsfonts}               % basic math fonts
\usepackage{amsmath}                % AMS math macros
\usepackage{amscd}                  % Commutative diagrams
\usepackage{amsopn}
\usepackage{graphicx}               % to insert figures
\usepackage{xcolor}                 % colors for e-copies
\usepackage{algpseudocode}          % pseudo code and algorithms
\usepackage{subcaption}             % subfigures
\usepackage{placeins}               % Float barriers
\usepackage{hyperref}               % PDF hyperreferences
\usepackage{booktabs}

\definecolor{applegreen}{rgb}{0.55, 0.71, 0.0}
\definecolor{blue(ncs)}{rgb}{0.0, 0.53, 0.74}
\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}

\DeclareMathOperator{\diag}{diag}

%--------------------------------  Preamble  -----------------------------------

\title{Local Fourier Analysis of Domain Decomposition and Multigrid Methods for High-Order Matrix-Free Finite Elements}

\author{Jeremy~L.}{Thompson}

\otherdegrees{B.S., United States Air Force Academy, 2009\\
	          M.Sc., University of Washington, 2011}

\degree{Doctor of Philosophy}       %  #1 {long descr.}
	   {Ph.D., Applied Mathematics} %  #2 {short descr.}

\dept{Department of}                %  #1 {designation}
	 {Applied Mathematics}          %  #2 {name}

\advisor{Prof.}                     %  #1 {title}
	    {Jed Brown}                 %  #2 {name}

\reader{Adrianna Gillman}           %  2nd person to sign thesis
\readerThree{Daniel Appel\"o}       %  3rd person to sign thesis
\readerFour{Ian Grooms}             %  4th person to sign thesis
\readerFive{Kenneth Jansen}         %  5th person to sign thesis

\abstract{ %\OnePageChapter	% if this abstract goes under 1 page
High-order matrix-free finite element operators offer superior performance on modern high performance computing hardware when compared to assembled sparse matrices, both with respect to floating point operations needed for operator evaluation and the memory transfer needed for a matrix-vector product.
However, high-order matrix-free operators require iterative solvers, such as Krylov subspace methods, and these methods converge slowly for ill-conditioned operators, such as high-order finite element operators.
Preconditioning techniques can significantly improve the convergence of these iterative solvers for high-order matrix-free finite element operators.
In particular, $p$-multigrid and domain decomposition methods are particularly well suited for problems on unstructured meshes, but these methods can involve parameters that require careful tuning to ensure proper convergence.
Local Fourier Analysis of these preconditioners analyzes the frequency modes found in the error following the application of these methods and can provide sharp convergence estimates and parameter tuning while only requiring computation on a single representative element or macro-element patch.

In this dissertation, we present a representation of arbitrary second-order partial differential equations for high-order finite element discretizations that facilitates matrix-free implementation.
This representation is used by the Center for Efficient Exascale Discretizations to provide performance portable high-order matrix-free implementations of finite element operators for arbitrary second order partial differential equations.

We develop Local Fourier Analysis of finite element operators and preconditioners described with this representation, focusing on multigrid and domain decomposition preconditioning techniques.

The Local Fourier Analysis of $p$-multigrid is validated with numerical experiments.
Furthermore, we extend this Local Fourier Analysis to reproduce previous work with $h$-multigrid by using macro-elements consisting of multiple low-order finite elements.

We also develop Fourier Analysis of the lumped and Dirichlet versions of Balancing Domain Decomposition by Constraints preconditioners.
By using Fast Diagonalization Method approximate subdomain solvers, the increased setup costs for the Dirichlet Balancing Domain Decomposition by Constraints preconditioner, relative to the lumped variant, can be substantially reduced, which makes Dirichlet Balancing Domain Decomposition by Constraints an attractive preconditioner.
We validate this work against previous numerical experiments on high-order finite elements, and we can exactly reproduce previous work on the Local Fourier Analysis of Balancing Domain Decomposition by Constraints by using macro-elements consisting of multiple low-order finite elements.

The performance of $p$-multigrid in parallel is partially determined by the number of multigrid levels.
A larger number of multigrid levels requires additional global communication on parallel machines, but aggressive coarsening is not supported by traditional polynomial smoothers, which leads to gaps in the error frequency modes targeted by the total multigrid method and degraded convergence.
Dirichlet Balancing Domain Decomposition by Constraints can be used as a smoother for $p$-multigrid to target a wider range of error mode frequencies than polynomial smoothers such as the Chebyshev semi-iterative method, which facilitates more aggressive coarsening.
We provide Local Fourier Analysis of $p$-multigrid with Dirichlet Balancing Domain Decomposition by Constraints smoothing to demonstrate the suitability of this combination for preconditioning high-order matrix-free finite element discretizations.
}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
This work is supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of two U.S. Department of Energy organizations (Office of Science and the National Nuclear Security Administration) responsible for the planning and preparation of a capable exascale ecosystem, including software, applications, hardware, advanced system engineering and early testbed platforms, in support of the nation’s exascale computing imperative.
}

%\ToCisShort % use this only for 1-page Table of Contents

%\LoFisShort % use this only for 1-page Table of Figures
% \emptyLoF  % use this if there is no List of Figures

%\LoTisShort % use this only for 1-page Table of Tables
% \emptyLoT  % use this if there is no List of Tables

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={LFA of Domain Decomposition and Multigrid Methods for High-Order Matrix-Free FEM},
  pdfauthor={Jeremy L Thompson}
}
\fi

%-------------------------------------------------------------------------------
%--------------------------------  Document  -----------------------------------
%-------------------------------------------------------------------------------

\begin{document}

\input macros.tex
\input 01-Introduction/introduction.tex
\input 02-HighOrderFEM/highorderfem.tex
\input 03-LocalFourierAnalysis/localfourieranalysis.tex
\input 04-MultigridMethods/multigridmethods.tex
\input 05-DomainDecomposition/domaindecomposition.tex
\input 06-Conclusions/conclusions.tex

%-------------------------------  Bibliography  --------------------------------
\bibliographystyle{plain}           % or "siam", or "alpha", etc.
\nocite{*}                          % list all refs in database, cited or not
\bibliography{references}           % Bib database in "refs.bib"

%--------------------------------  Appendices  ---------------------------------
%\appendix
%\input appendixA.tex
%\input appendixB.tex

\end{document}
%-------------------------------------------------------------------------------
